### 2014-06-25 ms/ms.Rmd
Refine paper

# *Ecological Archives* Exxxxx
# Falster D.S. *et al* BAAD: a Biomass And Allometry Database for woody plants. *Ecology* xxxx

```{r, results="hide", echo=FALSE, message=FALSE}
library(knitr, quietly=TRUE)
knitr::opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="")

library(plyr)
library(bibtex)
library(knitcitations)
library(Hmisc)
library(whisker)

bib <- read.bibtex("refs.bib")

source("MS-fun.R")
```

```{r, results="hide", echo=FALSE, message=FALSE}

baad <- readRDS("../output/baad.rds")
data <- baad$data

var.def <- read.csv("../config/variableDefinitions.csv",
                    stringsAsFactors=FALSE)
vars <- setdiff(var.def$Variable[var.def$Type == "numeric"], c("map","mat","lai","age"))
```

```{r,results="asis",echo=FALSE, message=FALSE}
writeLines(paste("**List of Authors:**", lisOfAuthors(baad$contact)))
```

@@

Quantifying the amount of mass or energy invested in plant tissues is of fundamental interest across a range of disciplines, including ecology, forestry, ecosystem science, and climate change science `r citep(list(bib["niklas_plant_1994"],bib["chave_tree_2005"], "10.1111/j.1365-2745.2010.01735.x"))`. The allocation of net primary production into different plant components is an important process affecting the lifetime of carbon in ecosystems, and resource use and productivity by plants  `r citep(list(bib["cannell_carbon_1994"],bib["litton_carbon_2007"],bib["poorter_biomass_2012"]))`. While many studies in have destructively harvested woody plants in the name of science, most of these data have only been made available in the form of summary tables or figures included in publications. Until now, the raw data has resided piecemeal on the hard drives of individual scientists spread around the world. Several studies have gathered together the fitted (allometric) equations for separate datasets `r citep(list("10.1016/S0378-1127(97)00019-4",bib["jenkins_national-scale_2003"],bib["zianis_biomass_2005"],"10.3832/ifor0901-006"))`, but none have previously attempted to organize and share the raw individual plant data underpinning these equations on a large scale. Gathered together, such data would represent an important resource for the community, meeting a widely recognised need for rich, open data resources to solve ecological problems `r citep(c("10.1016/j.tree.2013.05.002","10.1007/s13595-014-0375-3","10.1038/505160a"))`.

@@

@@

Identity:
Size:
Format and storage mode: ASCII text, comma delimited. Missing values
are denoted as 'NA'.

### B. Variable definitions

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
x <-daply(var.def, 1, function(x)
		paste0("* ", x$Variable,
		"\n\t- Label: ", x$label,
		"\n\t- Description: ", x$Description,
		"\n\t- Type: ", x$Type,
		"\n\t- Units: ", gsub(".","/", x$UnitsMD, fixed=TRUE)
		))

@@

```{r echo=FALSE, message=FALSE}

thesevars <- setdiff(var.def$Variable[var.def$Type=="numeric"],
                     c("map","mat","lai"))
Labels <- capitalize(var.def$label[var.def$Variable %in% thesevars])

Count_obs <- function(x)length(data[[x]][!is.na(data[[x]])])
N <- sapply(thesevars, Count_obs)

Count_studies <- function(x)length(unique(data[["studyName"]][!is.na(data[[x]])]))
Nstud <- sapply(thesevars, Count_studies)

df <- rbind.fill(apply(data[,thesevars], 2, function(x)data.frame(Min=min(x, na.rm=T),Max=max(x, na.rm=T),Median=median(x, na.rm=T))))

dfr <- data.frame(Variable=Labels, N=N)
dfr <- cbind(dfr,df)

dfr <- dfr[dfr$N > 0,]
rownames(dfr) <- NULL

f <- function(x)formatC(x, digits=2, format="fg")
dfr$Min <- f(dfr$Min)
dfr$Max <- f(dfr$Max)
dfr$Median <- f(dfr$Median)

```{r results='asis', echo=FALSE}
options(digits=9)
kable(dfr, "markdown", align="l", padding=10)
```

>>>>

---
output: html_document
---
# *Ecological Archives* Exxxxx
# Falster D.S. *et al* BAAD: a Biomass And Allometry Database for woody plants. *Ecology* xxxx

```{r, results="hide", echo=FALSE, message=FALSE}
source("MS-fun.R")

knitr::opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="")

bib <- read.bibtex("refs.bib")
baad <- readRDS("../output/baad.rds")
data <- baad$data
var.def <- read.csv("../config/variableDefinitions.csv",
                    stringsAsFactors=FALSE)

vars <- setdiff(var.def$Variable[var.def$Type == "numeric"], c("map","mat","lai","age"))
```

```{r,results="asis",echo=FALSE, message=FALSE}
writeLines(paste("**List of Authors:**", pasteC(listOfAuthors(baad$contact), ', ')))
```

@@

Quantifying the amount of mass or energy invested in plant tissues is of fundamental interest across a range of disciplines, including ecology, forestry, ecosystem science, and climate change science `r citep(list(bib["niklas_plant_1994"],bib["chave_tree_2005"], "10.1111/j.1365-2745.2010.01735.x"))`. The allocation of net primary production into different plant components is an important process affecting the lifetime of carbon in ecosystems, and resource use and productivity by plants  `r citep(list(bib["cannell_carbon_1994"],bib["litton_carbon_2007"],bib["poorter_biomass_2012"]))`. While many studies in have destructively harvested woody plants in the name of science, most of these data have only been made available in the form of summary tables or figures included in publications. Until now, the raw data has resided piecemeal on the hard drives of individual scientists spread around the world. Several studies have gathered together the fitted (allometric) equations for separate datasets `r citep(list("10.1016/S0378-1127(97)00019-4",bib["jenkins_national-scale_2003"],bib["zianis_biomass_2005"],"10.3832/ifor0901-006"))`, but none have previously attempted to organize and share the raw individual plant data underpinning these equations on a large scale. Gathered together, such data would represent an important resource for the community, meeting a widely recognised need for rich, open data resources to solve ecological problems `r citep(c("10.1016/j.tree.2013.05.002","10.1007/s13595-014-0375-3","10.1038/505160a", "10.1016/j.tree.2013.05.002"))`.

@@

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height8}

# World plot colored by vegetation type
cols <- make.transparent(c(
    "blue","brown","forestgreen","darkorange","dodgerblue2",
    "navajowhite4","lightgoldenrod3","lavender"),0.67)
vegs <- c("BorF","Sav","TempF","TempRF","TropRF","TropSF","Wo")
vegs_labels <- c("Boreal forest","Savannah","Temperate forest",
                 "Temperate rainforest","Tropical rainforest",
                 "Tropical seasonal forest","Woodland","Glasshouse / Common garden")

drawWorldPlot(data[data$vegetation == vegs[1],], sizebyn=TRUE, pchcol=cols[1])
for(i in 2:length(vegs)){
  drawWorldPlot(data[data$vegetation == vegs[i],], sizebyn=TRUE, pchcol=cols[i], add=TRUE)
}
drawWorldPlot(data[data$growingCondition == "GH",], sizebyn=TRUE,
              pchcol=cols[8], add=TRUE)
par(xpd=NA)
legend(-160, -100, vegs_labels[1:4], fill=cols[1:4], bty='n')
legend(-40, -100, vegs_labels[5:8], fill=cols[5:8], bty='n')

**Figure 1** Global distribution of studies included in BAAD. Symbols are sized relative to the number of individual plants in each dataset.

@@

BAAD contains the following files:

- `dictionary.csv`: a table of variable definitions
- `data.csv`: amalgamated dataset, with columns as defined in `dictionary.csv`
- `references.bib`: bibtex entries containing the primary source for each study
- `references.csv`: summary of bibtex file, giving DOI, URL and citation of  the primary source for each study
- `contacts.csv`: list of contacts and affiliations for each study

### B. Variable definitions for data.csv

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
x <-daply(var.def, 1, function(x)
		paste0("* ", x$Variable,
    "\n\t- Type: ", x$Type,
		"\n\t- Label: ", x$label,
		"\n\t- Description: ", x$Description,
		"\n\t- Units: ", gsub(".","/", x$UnitsMD, fixed=TRUE)
		))

@@

```{r results='asis', echo=FALSE, warning=FALSE}
options(digits=9)
kable(summaryTable(data, var.def), "markdown", align="l", padding=10)
```
